The problem and promise of scale in multilayer networks

### 2019-09-11 paper/introduction.Rmd
start box1

Two main types of multilayer networks exist: multiplex networks and interconnected networks. Layers in multiplex networks consist of the same entities with each layer representing either a different type of interaction (as in multirelational networks) or a different time point or window (as in temporal networks). Layers in interconnected networks consist of the same or different entities with layers representing different subsystems (as in networks of networks), different types of entities (as in intercontextual networks), or different spatial locations (as in spatial networks).

@@

>>>>

Two main types of multilayer networks exist: multiplex networks and interconnected networks. Layers in multiplex networks consist of the same entities with each layer representing either a different type of interaction (as in multirelational networks) or a different time point or window (as in temporal networks). Layers in interconnected networks consist of the same or different entities with layers representing different subsystems (as in networks of networks), different types of entities (as in intercontextual networks), or different spatial locations (as in spatial networks) [@finn2019].

@@

# Box 1: Types of spatiotemporally explicit data

Spatial data can be

how associations are measured: e.g. spatsoc
how relocations are categorized: e.g. landcover

Multilayer networks incoroprate spatial variables in two ways:
1. for determining association between individuals in a social system
1. for characterizing the spatial context of social systems

For example, association between individuals can be determined using georeferenced biologging devices such as radio‐frequency identification tags, radiotelemetry, and global positioning system (GPS) devices. Proximity based social networks (PBSNs) are association networks based on close proximity between individuals [@spiegel2016].

# References
